Staged Abstract Interpreters

### 2019-09-08 paper/20_prelim.tex
Typo

\paragraph{The Interpreter} Now we can construct the semantics-agnostic interpreter
in monadic form, shown in Figure \ref{fig:shared_int}. The basic idea
of a generic interpretation is to traverse the abstract syntax tree
while maintaining the effects such as environment and state updates.
Note that the interpreter is written in open-recursive style -- it cannot
refer to itself directly. Instead, @eval@ takes an additional parameter @ev@ of
type @Expr => Ans@ that refers to itself. Consequently, the method @close@ that
lifts lambda terms to closures and method @ap_clo@ that applies functions also
takes an extra @ev@, because evaluations may happen inside of them.
To close the open recursion, we use a fixed-point operator @fix@.
For concrete-interpretation instantiation, @fix@ works like the Y combinator;
for abstract-interpretation instantiation, it will instrument the interpreter
by memoizing @ev@'s inputs and outputs, which ensures the termination of
abstract interpretation.
Finally, there is a top-level wrapper @run@. The return type @Result@
depends on the kind of monads being used; and therefore is also left abstract.
\begin{lstlisting}
  def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans
  type Result; def run(e: Expr): Result
\end{lstlisting}

>>>>

\paragraph{The Interpreter} We can now construct the semantics-agnostic interpreter
in monadic form, shown in Figure \ref{fig:shared_int}. The basic idea
of generic interpretation is to traverse the abstract syntax tree
while maintaining the effects (such as environment and state updates).
Note that the interpreter is written in open-recursive style -- it cannot
refer to itself directly. Instead, @eval@ takes an additional parameter @ev@ of
type @Expr => Ans@ that refers to itself. Consequently, the method @close@ that
lifts lambda terms to closures and method @ap_clo@ that applies functions also
takes an extra @ev@, because evaluations may happen inside of them.
To close the open recursion, we use a fixed-point operator @fix@.
For concrete-interpretation instantiation, @fix@ works like the Y combinator;
for abstract-interpretation instantiation, it will instrument the interpreter
by memoizing @ev@'s inputs and outputs, which ensures the termination of
abstract interpretation.
Finally, there is a top-level wrapper @run@. The return type @Result@
depends on the kind of monads being used; and therefore is also left abstract.
\begin{lstlisting}
  def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans
  type Result; def run(e: Expr): Result
\end{lstlisting}
